Titeln på avhandlingens språk

### 2023-03-27 body/part1/chapter1-introduction/introduction.tex
still working on intro

>>>>

One of the main challenges to the study of latency-sensitive applications such as \gls{CPS} and \gls{MAR} on Edge Computing is that these applications interact with the real world, and thus must be studied in real-time.
This implies that any study of these applications must be done in an environment that accurately reflects the real-world conditions in which they are deployed.
Unfortunately, replicating these conditions in a controlled experimental environment is difficult and often leads to inconsistencies in results, and traditional methods that rely on simulations may not be sufficient to accurately capture and evaluate the performance of these applications in real-world scenarios.

The scalability of studying these systems is also a challenge.
It may not be feasible for researchers to test the applications on a large scale due to limitations in access to specialized equipment, personnel and test subjects, as well as facilities.
\glspl{CPS} often rely on physical sensors and actuators, making it difficult to replicate real-world conditions in a controlled environment at scale, and conducting experiments involving human subjects for \gls{MAR} is time-consuming and expensive.

The highly complex effects on the wireless network is another major challenge to studying latency-sensitive applications on Edge Computing.
The presence of multiple devices accessing the network simultaneously can result in interference, network congestion, and other factors that can affect the performance of the system.
These effects are difficult to simulate and/or emulate, particularly in multi-tenant deployments, where each tenant may have different requirements and resource usage patterns.

Finally, the combination of the characteristics enumerated above makes the study of these applications hard to automate, making it challenging to conduct large-scale experiments or to collect data over an extended period of time.
\gls{CPS} and \gls{MAR} applications are highly dynamic and adaptive, and their behavior cannot be easily predicted.
Moreover, there is often a significant amount of variability in the behavior of different components of the application, such as sensors, actuators, and network connections, which makes it difficult to automate the testing process.
